# Ineqaulity task - week 4

#### task: Join the global gender inequality index to spatial data of the World, creating a new column of difference in inequality between 2010 and 2019. Share it with the World on GitHub. Add you repository URL to the circulated spreadsheet

## Reproduce

### package versions

```{r first, eval=FALSE}
# i have taken a snapshot with
#renv::snapshot()

#install the same packages
#renv::restore()
```

### Read in data:

Located within the Data folder:

-   HDI data from: <http://hdr.undp.org/en/indicators/68606#>
-   Shapefile from: <https://hub.arcgis.com/datasets/2b93b06dc0dc4e809d3c8db5cb96ba69_0/explore?location=-2.688200%2C0.000000%2C1.41>

## Load packages

```{r}
library(tidyverse)
library(sf)
library(here)
library(janitor)
library(countrycode)
```

```{r reand in datas}
HDI <- read_csv(here::here("wk4","Gender Inequality Index (GII).csv"),
                locale = locale(encoding = "latin1"),
                na = "..", skip=5)

World <- st_read(here::here("wk4", "World_Countries_(Generalized)",
                            "World_Countries__Generalized_.shp"))
```

## Column names

Select columns we want and change country name to country code, using the `countrycode` package

We could also just join it without this on the country name column

```{r}
HDIcols<- HDI %>%
  clean_names()%>%
  select(country, x2019, x2010)%>%
  mutate(difference=x2019-x2010)%>%
  slice(1:189,)%>%
  mutate(iso_code=countrycode(country, origin = 'country.name', destination = 'iso2c'))
  

#this was just a test. hello
#t <- countrycode(HDIcols$country, origin = 'country.name', destination = 'iso2c') 

```

## Join
Now both .csv&.shp have the mutual col of 'ISO'.
Join the csv to world shape file

```{r}
Join_HDI <- World %>% 
  clean_names() %>%
  left_join(., 
            HDIcols,
            by = c("aff_iso" = "iso_code"))
```

...next time we will make a map using different repos

lovcal change


### Share it with the World on GitHub

### Add you repository URL to the circulated spreadsheet